MSstatsPTM_SImulation_Analysis

### 2021-09-16 code/MSstatsPTM_Simulation_Analysis.Rmd
Added Shigella and USP30 details to supplmentary

## Define metrics
calculate_summary_stats <- function(df, protein_col_name, pval_col_name, sd, rep, conditions){
  fpr <- df %>% filter(get(pval_col_name) < .05 & grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(grepl("NoChange", get(protein_col_name))))
  sensitivity <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(!grepl("NoChange", get(protein_col_name))))
  specificity <- df %>% filter(get(pval_col_name) >= .05 & grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(grepl("NoChange", get(protein_col_name))))
  precision <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(get(pval_col_name) < .05))
  accuracy <- df %>% filter((get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) | 
                              (get(pval_col_name) >= .05 & grepl("NoChange", get(protein_col_name)))) %>% 
    nrow() / nrow(df)
  recall <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / df %>% filter(!grepl("NoChange", get(protein_col_name))) %>% nrow()
  results_temp <- data.table(fpr = fpr, sensitivity = sensitivity, 
                             specificity = specificity, precision = precision, 
                             sd = sd, rep = rep, conditions = conditions,
                             accuracy = accuracy, recall = recall)
  return(results_temp)
}
```

@@

load(file = "model_data/ptm_models_sim1.rda")#ptm_models_sim1
load(file = "model_data/adjusted_models_sim1.rda")#adjusted_models_sim1 
load(file = "model_data/ttest_models_sim1.rda")#ttest_sim1
load(file = "model_data/adj_ttest_models_sim1.rda")#adj_ttest_sim1
load(file = "model_data/limma_models_sim1.rda")#limma_results_sim1
load(file = "model_data/adj_limma_models_sim1.rda")#adj_limma_sim1

@@

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 7, fig.height = 6}
png("supplementary/sim_new/sim1_FDR_all_models.png", width = 750, height = 500)

models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  ggplot() + geom_point(aes(x = Model, y = fpr, size = Replicates, color = Model)) + 
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: FDR all models", x = "Model", y = "FDR")

@@

``` {r, echo = FALSE, message=FALSE, warning=FALSE}
png("supplementary/sim_new/sim1_FDR.png", width = 750, height = 500)

models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = fpr, size = Replicates, color = Model)) + 
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: FDR adjusted models", x = "Model", y = "FDR")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("supplementary/sim_new/sim1_Recall.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = recall, size = Replicates, color = Model)) + 
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: Recall adjusted models", x = "Model", y = "Recall")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("supplementary/sim_new/sim1_accuracy.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: Accuracy adjusted models", x = "Model", y = "Accuracy")

@@

boxplot_data <- data.table()
for (i in seq_len(nrow(param_combos))){
  temp1 <- adjusted_models_sim1[[i]] %>% filter(!grepl("NoChange", Protein) & Label %in% conds)
  temp1$Model <- "Proposed"
  temp1$log2FC <- temp1$log2FC*-1
  temp2 <- adj_ttest_sim1[[i]] %>% filter(!grepl("NoChange", ptm) & label %in% conds) %>% rename(log2FC = estimate, Label = label)
  temp2$Model <- "T-test"
  temp3 <- adj_limma_sim1[[i]] %>% filter(!grepl("NoChange", PTM) & Label %in% cond2) %>% rename(log2FC = Log2FC)
  temp3$Model <- "Limma"
  temp3$log2FC <- temp3$log2FC*-1

@@

png("supplementary/sim_new/sim1_FC_boxplot.png", width = 750, height = 500)
boxplot_data %>% mutate(Model = factor(Model, levels=c("Proposed", "Limma", "T-test")),
                        reps = factor(reps, levels = c(2,3,5,10))) %>% 
  ggplot()  + geom_hline(yintercept = .75, color = "red", size = 1.1) + 
  geom_boxplot(aes(y = log2FC, x = reps, fill = Model)) + facet_grid(vars(sd), vars(cond)) + 
  theme_bw() +
  theme(axis.text.x = element_text(size = 12), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: Fold Change Distribution", x = "Replicates", y = "Log2FC")
dev.off()
```

@@

load(file = "model_data/ptm_models_sim3.rda")#ptm_models_sim1
load(file = "model_data/adjusted_models_sim3.rda")#adjusted_models_sim1 
load(file = "model_data/ttest_models_sim3.rda")#ttest_sim1
load(file = "model_data/adj_ttest_models_sim3.rda")#adj_ttest_sim1
load(file = "model_data/limma_models_sim3.rda")#limma_results_sim1
load(file = "model_data/adj_limma_models_sim3.rda")#adj_limma_sim1

@@

``` {r, echo = FALSE, message=FALSE, warning=FALSE}
png("supplementary/sim_new/sim3_FDR.png", width = 350, height = 350)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = fpr, size = Replicates, color = Model)) + 
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "FDR adjusted models", x = "Model", y = "FDR")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("supplementary/sim_new/sim3_Recall.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = recall, size = Replicates, color = Model)) + 
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 2: Recall adjusted models", x = "Model", y = "Recall")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("supplementary/sim_new/sim3_Accuracy.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 2: Accuracy adjusted models", x = "Model", y = "Accuracy")
dev.off()
```

@@

boxplot_data <- data.table()
for (i in seq_len(nrow(param_combos))){
  temp1 <- adjusted_models_sim3[[i]] %>% filter(!grepl("NoChange", Protein) & Label %in% conds)
  temp1$Model <- "Proposed"
  temp1$log2FC <- temp1$log2FC*-1
  temp2 <- adj_ttest_sim3[[i]] %>% filter(!grepl("NoChange", ptm) & label %in% conds) %>% rename(log2FC = estimate, Label = label)
  temp2$Model <- "T-test"
  temp3 <- adj_limma_sim3[[i]] %>% filter(!grepl("NoChange", PTM) & Label %in% cond2) %>% rename(log2FC = Log2FC)
  temp3$Model <- "Limma"
  temp3$log2FC <- temp3$log2FC*-1

@@

png("supplementary/sim_new/sim3_FC_boxplot.png", width = 750, height = 500)
boxplot_data %>% mutate(Model = factor(Model, levels=c("Proposed", "Limma", "T-test")),
                        reps = factor(reps, levels = c(2,3,5,10))) %>% 
ggplot()  + geom_hline(yintercept = .75, color = "red", size = 1.1) + 
geom_boxplot(aes(y = log2FC, x = reps, fill = Model)) + facet_grid(vars(sd), vars(cond)) + 
  theme_bw() +
  theme(axis.text.x = element_text(size = 12), 
                                               axis.text.y = element_text(size = 12), 
                                               legend.text=element_text(size=12),
                                               axis.title.y = element_text(size = 14),
                                               axis.title.x = element_text(size = 14),
                                               title = element_text(size = 16),
                                               strip.text = element_text(size = 12)) + 
labs(title = "Simulation 2: Fold Change Distribution", x = "Replicates", y = "Log2FC")
dev.off()
```

>>>>

## Define metrics
calculate_summary_stats <- function(df, protein_col_name, pval_col_name, sd, rep, conditions){
  fpr <- df %>% filter(get(pval_col_name) < .05 & grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(get(pval_col_name) < .05))
  sensitivity <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(!grepl("NoChange", get(protein_col_name))))
  specificity <- df %>% filter(get(pval_col_name) >= .05 & grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(grepl("NoChange", get(protein_col_name))))
  precision <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(get(pval_col_name) < .05))
  accuracy <- df %>% filter((get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) | 
                              (get(pval_col_name) >= .05 & grepl("NoChange", get(protein_col_name)))) %>% 
    nrow() / nrow(df)
  recall <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / df %>% filter(!grepl("NoChange", get(protein_col_name))) %>% nrow()
  results_temp <- data.table(fpr = fpr, sensitivity = sensitivity, 
                             specificity = specificity, precision = precision, 
                             sd = sd, rep = rep, conditions = conditions,
                             accuracy = accuracy, recall = recall)
  return(results_temp)
}
```

@@

load(file = "../data/ptm_models_sim1.rda")#ptm_models_sim1
load(file = "../data/adjusted_models_sim1.rda")#adjusted_models_sim1 
load(file = "../data/ttest_models_sim1.rda")#ttest_sim1
load(file = "../data/adj_ttest_models_sim1.rda")#adj_ttest_sim1
load(file = "../data/limma_models_sim1.rda")#limma_results_sim1
load(file = "../data/adj_limma_models_sim1.rda")#adj_limma_sim1

@@

cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")
cbPalette_first <- c("#E69F00", "#F0E442", "#56B4E9", "#0072B2", "#009E73", "#D55E00", "#CC79A7", "#999999")
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 7, fig.height = 6}
png("../supplementary/sim_new/sim1_FDR_all_models.png", width = 750, height = 500)

models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  ggplot() + geom_point(aes(x = Model, y = fpr, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette_first) +
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: FDR all models", x = "Model", y = "FDR")

@@

``` {r, echo = FALSE, message=FALSE, warning=FALSE}
png("../supplementary/sim_new/sim1_FDR.png", width = 750, height = 500)

models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = fpr, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: FDR adjusted models", x = "Model", y = "FDR")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("../supplementary/sim_new/sim1_Recall.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = recall, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: Recall adjusted models", x = "Model", y = "Recall")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("../supplementary/sim_new/sim1_accuracy.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed no Adjustment", "Limma", 
                                               "Limma no Adjustment", "T-Test", "T-Test no Adjustment")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: Accuracy adjusted models", x = "Model", y = "Accuracy")

@@

boxplot_data <- data.table()
for (i in seq_len(nrow(param_combos))){
  temp1 <- adjusted_models_sim1[[i]] %>% filter(!grepl("NoChange", Protein) & Label %in% conds)
  temp1$Model <- "Proposed"
  temp1$log2FC <- temp1$log2FC*-1
  temp2 <- adj_ttest_sim1[[i]] %>% filter(!grepl("NoChange", ptm) & label %in% conds)
  temp2 <- setNames(temp2, c("ptm", "Label", "pval", "tstat", "SE", "df", "log2FC"))
  temp2$Model <- "T-test"
  temp3 <- adj_limma_sim1[[i]] %>% filter(!grepl("NoChange", PTM) & Label %in% cond2) 
  temp3 <- setNames(temp3, c('PTM', 'Label', 'log2FC', 'pvalue', 'df', 'se'))
  temp3$Model <- "Limma"
  temp3$log2FC <- temp3$log2FC*-1

@@

png("../supplementary/sim_new/sim1_FC_boxplot.png", width = 750, height = 500)
boxplot_data %>% mutate(Model = factor(Model, levels=c("Proposed", "Limma", "T-test")),
                        reps = factor(reps, levels = c(2,3,5,10))) %>% 
  ggplot()  + geom_hline(yintercept = .75, color = "red", size = 1.1) + 
  geom_boxplot(aes(y = log2FC, x = reps, fill = Model)) + facet_grid(vars(sd), vars(cond)) + 
  scale_fill_manual(values=cbPalette) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 1: Fold Change Distribution", x = "Replicates", y = "Log2FC")
dev.off()
```

@@

load(file = "../data/ptm_models_sim3.rda")#ptm_models_sim1
load(file = "../data/adjusted_models_sim3.rda")#adjusted_models_sim1 
load(file = "../data/ttest_models_sim3.rda")#ttest_sim1
load(file = "../data/adj_ttest_models_sim3.rda")#adj_ttest_sim1
load(file = "../data/limma_models_sim3.rda")#limma_results_sim1
load(file = "../data/adj_limma_models_sim3.rda")#adj_limma_sim1

@@

``` {r, echo = FALSE, message=FALSE, warning=FALSE}
png("../supplementary/sim_new/sim3_FDR.png", width = 350, height = 350)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = fpr, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "FDR adjusted models", x = "Model", y = "FDR")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("../supplementary/sim_new/sim3_Recall.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = recall, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 2: Recall adjusted models", x = "Model", y = "Recall")
dev.off()
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
png("../supplementary/sim_new/sim3_Accuracy.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("Proposed", "Proposed_no_adj", "limma_no_adj", 
                                               "Limma", "ttest_no_adj", "T-Test")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("Proposed", "T-Test", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  facet_grid(vars(sd), vars(conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_blank(), 
                                                 axis.text.y = element_text(size = 12), 
                                                 legend.text=element_text(size=12),
                                                 axis.title.y = element_text(size = 14),
                                                 axis.title.x = element_text(size = 14),
                                                 title = element_text(size = 16),
                                                 strip.text = element_text(size = 12)) + 
  labs(title = "Simulation 2: Accuracy adjusted models", x = "Model", y = "Accuracy")
dev.off()
```

@@

boxplot_data <- data.table()
for (i in seq_len(nrow(param_combos))){
  temp1 <- adjusted_models_sim3[[i]] %>% filter(!grepl("NoChange", Protein) & Label %in% conds)
  temp1$Model <- "Proposed"
  temp1$log2FC <- temp1$log2FC*-1
  temp2 <- adj_ttest_sim3[[i]] %>% filter(!grepl("NoChange", ptm) & label %in% conds)
  temp2 <- setNames(temp2, c("ptm", "Label", "pval", "tstat", "SE", "df", "log2FC"))
  temp2$Model <- "T-test"
  temp3 <- adj_limma_sim3[[i]] %>% filter(!grepl("NoChange", PTM) & Label %in% cond2) 
  temp3 <- setNames(temp3, c('PTM', 'Label', 'log2FC', 'pvalue', 'df', 'se'))
  temp3$Model <- "Limma"
  temp3$log2FC <- temp3$log2FC*-1

@@

png("../supplementary/sim_new/sim3_FC_boxplot.png", width = 750, height = 500)
boxplot_data %>% mutate(Model = factor(Model, levels=c("Proposed", "Limma", "T-test")),
                        reps = factor(reps, levels = c(2,3,5,10))) %>% 
ggplot()  + geom_hline(yintercept = .75, color = "red", size = 1.1) + 
geom_boxplot(aes(y = log2FC, x = reps, fill = Model)) + facet_grid(vars(sd), vars(cond)) + 
    scale_fill_manual(values=cbPalette) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12), 
                                               axis.text.y = element_text(size = 12), 
                                               legend.text=element_text(size=12),
                                               axis.title.y = element_text(size = 14),
                                               axis.title.x = element_text(size = 14),
                                               title = element_text(size = 16),
                                               strip.text = element_text(size = 12)) + 
labs(title = "Simulation 2: Fold Change Distribution", x = "Replicates", y = "Log2FC")
dev.off()
```
